%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{W\MakeLowercase{illiam} Y. L\MakeLowercase{ee}} % Your name
%\address{500 College Ave, Swarthmore, PA} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\url{cs.swarthmore.edu/~wlee1} \\ williamylee@google.com \\ \url{linkedin.com/in/williamylee}} % Your phone number and email

\definecolor{linkblue}{HTML}{007bff}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	{ \textbf{Swarthmore College} (B.A., Computer Science)} \hfill {\em Class of 2020} \\
	\null \hfill {\em GPA: 3.87, Phi Beta Kappa}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
	{
		\begin{rSubsection}{Behavior Prediction,  Waymo}{\em August 2020 - Present}{}{}
			--- Machine learning for behavior prediction at Waymo (formerly Google's self-driving car project). \\
			--- Advance the state of the art of machine learning and deep learning to predict the future behavior of other vehicles, cyclists, and pedestrians on the road. \\
			--- Led the transition to the next-generation behavior prediction tech stack on Waymo's trucks.
		\end{rSubsection}
	}
\end{rSection}  % End Work Experience.
\begin{rSection}{Internship Experience}
	{
		\begin{rSubsection}{Behavior Prediction,  Waymo}{\em Summer 2019}{}{}
			% --- Spent a summer developing machine learning models for the Waymo driver (formerly Google's self-driving car project). \\
			--- Developed machine learning models for the Waymo driver (formerly Google's self-driving car project) on the behavior prediction team. \\
			--- Internship featured on \href{https://blog.waymo.com/2019/12/from-hosted-to-host-internship.html}{\color{linkblue}{\underline{Waymo's public blog}}}.
		\end{rSubsection}
	}
	{
		\begin{rSubsection}{Search Relevance, Salesforce}{\em Summer 2018}{}{}
			--- Redesigned the search metrics pipeline for Salesforce Search using Splunk and Hadoop. \\
			--- Data analysis on terabyte-scale logs to develop high quality metrics measuring Salesforce Search's performance.
			% --- Performed data analysis on terabyte-scale logs and developed high quality metrics measuring Salesforce Search's performance.
		\end{rSubsection}
	}
	{
		\begin{rSubsection}{Laboratory for Advanced Sensing, NASA Ames}{\em Summers 2016 and Summer 2017}{}{}
			--- Designed and implemented a computer vision alignment pipeline to fully georectify 4k drone footage onto NASA satellite imagery. \\
			--- Implemented a sliding window CNN using Keras to classify coral reef morphology. \\
			--- Developed a entropy-based adaptive gaussian blur module for NASA's stereogammetry suite.
		\end{rSubsection}
	}

\end{rSection}  % End Work Experience.

\begin{rSection}{Academic Experience}
	{\textbf{St. Anne's College, University of Oxford} Visiting student at the University of Oxford for the 2018--2019 academic year in the mathematics and computer science departments. Includes graduate level coursework in Advanced Machine Learning and Randomized Algorithms.}

	{\textbf{Research Assistant, Biomedical Machine Learning Lab} Research assistant working with Professor Ameet Soni on weakly supervised learning. Established baselines (class activation maps), conducted literature review, and implemented state-of-the-art techniques in weakly supervised object localization. Finetuned models to the CheXpert Chext X-ray prediction task.}
\end{rSection}  % End Academic Experience.

\begin{rSection}{Coursework}  %  Begin Coursework.
	{
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			University of Oxford \ & Advanced Machine Learning, Probability \& Computing, \\ \ & Probability, Artificial Intelligence, Statistics \\

			Swarthmore College \ & Machine Learning, Computer Vision, Bioinformatics \\
		\end{tabular}
	}
\end{rSection}  % End Coursework.

\begin{rSection}{Skills}
	{Python, PyTorch/TensorFlow, C++, Java, OpenCV, SciPy, Hadoop/Splunk, Linux, SQL}
\end{rSection}  % End Skills.

\end{document}
