%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{url}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{W\MakeLowercase{illiam} L\MakeLowercase{ee}} % Your name
\address{St. Anne's College, Oxford, UK} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\url{cs.swarthmore.edu/~wlee1} \\ wlee1@swarthmore.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	{ \textbf{Palo Alto High School}} \hfill {\em 2016 (3.97/4.00)} 

	{ \textbf{St. Anne's College, Oxford} (Maths, Computer Science)} \hfill {\em 2018 -- Present} 

	{ \textbf{Swarthmore College} (Maths, Computer Science)} \hfill {\em 2020 expected (3.9+)} 
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
	{
		\begin{rSubsection}{Search Relevance, Salesforce}{\em Summer 2018}{}{}
			--- Redesigned the search metrics pipeline for Salesforce Search Cloud using Splunk and Hadoop. \\
			--- Data analysis on terabyte-scale logs to accurately measure Salesforce Search's performance.
		\end{rSubsection}
	
	}
	{
		\begin{rSubsection}{Laboratory for Advanced Sensing, NASA Ames}{\em Summer 2017}{}{}
			--- Designed and implemented a computer vision alignment pipeline to fully georectify 4k UAV footage onto satellite imagery. \\
			--- Implemented a sliding window CNN using Keras to classify coral reef morphology (baseline model).
		\end{rSubsection}
	}

	{
		\begin{rSubsection}{Intelligent Robotics Group, NASA Ames}{\em Summer 2016}{}{}
			--- Developed a entropy-based adaptive gaussian blur module for NASA's stereogammetry suite. \\
			--- Full stack web development on NASA's GeoCam space project and xGDS mission planning software.
		\end{rSubsection}
	}
\end{rSection}  % End Work Experience.


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
	{\textbf{Synthetic Datasets Using Deep Generative Models}
	\\Explored training neural networks on Synthetic Datasets created by Deep Generative Models (GANs, Deep Boltzmann Machines) for my final project in machine learning, with two group members. Created synthetic datasets for MNIST and CIFAR-10 datasets and analyzed efficacy of models trained on  generated datasets. \\}
\\
	{\textbf{Capturing Population Events Using HMMs}
	\\Analyzed genomic sequence data from different human populations in the 1000 Genomes Project. Combined multiple projects from a semester-long Bioinformatics class to create an end-to-end genomic pipeline to convert raw sequence data to population-size estimates using TMRCA. Successfully captured the out-of-Africa bottleneck; concluded that smaller-scale population events require more data. \\}
\\
	{\textbf{Weight Uncertainty in Neural Networks (in progress)}\\
	Working on replicating and extending the results found in \textit{Weight Uncertainty in Neural Networks (Blundell et al., 2015)}.}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Coursework}  %  Begin Coursework.
	{
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			University of Oxford \ & Advanced Machine Learning, Probability \& Computing, \\ \ & Probability, Artificial Intelligence \\

			Swarthmore College \ & Machine Learning, Computer Vision, Bioinformatics \\
		\end{tabular}
	}
\end{rSection}  % End Coursework.

\begin{rSection}{Skills}
	{Python, Pytorch/TensorFlow, OpenCV, Sklearn, Java/C++/C, Hadoop/Splunk, Photography, Math}
\end{rSection}








%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{wtf is this sec} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}

